\def\aciee{Angew.~Chem.~Int.~Ed.~Engl.}
\def\acp{Adv.~Chem.~Phys.}
\def\acr{Acc.~Chem.~Res.}
\def\ac{Acta.~Crystallogr.}
\def\ajp{Am.~J.~Phys.}
\def\am{Adv.~Mater.}
\def\apl{Appl.~Phys.~Lett.}
\def\ap{Ann.~Physik}
\def\Pa{Physica A}
\def\arpc{Ann.~Rev.~Phys.~Chem.}
\def\bbpc{Ber. Bunsenges. Phys. Chem.}
\def\bc{Biochemistry}
\def\cccc{Coll.~Czech.~Chem.~Comm.}
\def\cj{Comput.~J.}
\def\cpc{Comp.~Phys.~Comm.}
\def\cpl{Chem.~Phys.~Lett.}
\def\cp{Chem.~Phys.}
\def\crev{Chem.~Rev.}
\def\dalton{J.~Chem.~Soc., Dalton Trans.}
\def\el{Europhys.~Lett.}
\def\faraday{J.~Chem.~Soc., Faraday Trans.}
\def\fartrans{J.~Chem.~Soc., Faraday Trans.}
\def\fdisc{J.~Chem.~Soc., Faraday Discuss.}
\def\ic{Inorg.~Chem.}
\def\ijmpc{Int.~J.~Mod.~Phys.~C}
\def\ijqc{Int.~J.~Quant.~Chem.}
\def\jacers{J. Am. Ceram. Soc.}
\def\jacs{J.~Am.~Chem.~Soc.}
\def\jap{J.~Appl.~Phys.}
\def\jas{J.~Atmos.~Sci.}
\def\jcc{J.~Comp.~Chem.}
\def\jce{J.~Chem.~Ed.}
\def\jcis{J.~Colloid Interface Sci.}
\def\jcp{J.~Chem.~Phys.}
\def\jcscc{J.~Chem.~Soc., Chem.~Commun.}
\def\jcsft{J.~Chem.~Soc., Faraday Trans.}
\def\jetp{J.~Exp.~Theor.~Phys.~(Russia)}
\def\jmc{J.~Math.~Chem.}
\def\jmsp{J.~Mol.~Spec.}
\def\jmst{J.~Mol.~Structure}
\def\jncs{J.~Non-Cryst.~Solids}
\def\jpa{J.~Phys.~A}
\def\jphysc{J.~Phys.~C}
\def\jpca{J.~Phys.~Chem.~A}
\def\jpcb{J.~Phys.~Chem.~B}
\def\jpcm{J.~Phys.~Condensed Matter.}
\def\jpcssp{J.~Phys.~C: Solid State Phys.}
\def\jpcs{J.~Phys.~Chem.~Solids.}
\def\jpc{J.~Phys.~Chem.}
\def\jpfmp{J.~Phys.~F, Metal Phys.}
\def\jpsj{J.~Phys.~Soc.~Jpn.}
\def\jsp{J.~Stat.~Phys.}
\def\mg{Math.~Gazette}
\def\molphys{Mol.~Phys.}
\def\molp{Mol. Phys.}
\def\mrsb{Mater.~Res.~Soc.~Bull.}
\def\msr{Mater.~Sci.~Rep.}
\def\nat{Nature}
\def\njc{New J.~Chem.}
\def\pac{Pure.~Appl.~Chem.}
\def\phys{Physics}
\def\pla{Phys.~Lett.~A}
\def\phm{Philos. Mag.}
\def\pma{Philos.~Mag.~A}
\def\pmb{Philos.~Mag.~B}
\def\pml{Philos.~Mag.~Lett.}
\def\pnasu{Proc.~Natl.~Acad.~Sci.~USA}
\def\pnas{Proc.\ Natl.\ Acad.\ Sci.\  USA}
\def\pra{Phys.~Rev.~A}
\def\prbcm{Phys.~Rev.~B}
\def\prb{Phys.~Rev.~B}
\def\prc{Phys.~Rev.~C}
\def\prd{Phys.~Rev.~D}
\def\prep{Phys.~Reports}
\def\pre{Phys.~Rev.~E}
\def\prl{Phys.~Rev.~Lett.}
\def\prsa{Proc.~R.~Soc.~A}
\def\pr{Phys.~Rev.}
\def\psfg{Proteins: Struct., Func.~and Gen.}
\def\pssb{Phys.~State Solidi B}
\def\pss{Phys.~State Solidi}
\def\rmp{Rev.~Mod.~Phys.}
\def\rpp{Rep.~Prog.~Phys.}
\def\sci{Science}
\def\ss{Surf.~Sci.}
\def\tca{Theor.~Chim.~Acta}
\def\tetra{Tetrahedron}
\def\zfpd{Z.~Phys.~D}
\def\zpb{Z.~Phys.~B.}
\def\zpc{Z.~Phys.~Chem.}
\def\zpdamc{Z.~Phys.~D}
\def\zpd{Z.~Phys.~D}
